### 2020-03-25 paper/introduction.tex
after Andrei's comments

At the Beginning of Life (BOL), MSRs are commonly loaded with more
fuel than that required to achieve criticality (necessary for long-term core 
operation); this leads to excess reactivity at the BOL. Recent studies on MSRs showed that this excess reactivity 
at the BOL is large for many refueling scenarios and may reach $\approx$ $8100$ $pcm$
\cite{rykhlevskii2019modeling,betzler2016modeling,ashraf2020Strategies,ashraf2018nuclear,ashraf2020whole,ashraf2019modeling}.
Additionally, during burnup, online reprocessing and refueling system helps to control the reactivity of 
the MSRs \cite{ashraf2020whole,ashraf2019Preliminary}. However, the most common and reliable procedure 
to control the reactor is to insert or withdraw control rods made of material 
with a large neutron absorption cross section (e.g., boron, cadmium) 
\cite{duderstadt650nuclear}. 
Insertion of control rods introduces negative reactivity into the 
core which helps to compensate the excess reactivity and 
adjust the power level of the core or shut down the reactor in case of 
emergency \cite{glasstone1967nuclear}. Therefore, we should estimate 
the reactivity worth of the control rods 
\cite{varvayanni2009estimation,fadaei2009control,aoyama2007core,bretscher1997computing}.
 The reactivity worth of control rods correlates with the interference 
(shadowing effects) between control rod clusters 
\cite{girardin2008development,vcerba2017optimization}. 
The control rod worth and its efficiency to absorb excess positive reactivity is a subject of major interest since it directly affects reactor safety \cite{liu2018criticality,atkinson2019small,vcerba2017optimization,do2019criticality,guo2019advanced,varvayanni2009estimation}.

@@

Xuemei \emph{et al.} (2013) calculated the control worth in the thorium molten salt
reactor by using MCNP5 \cite{briesmeister2000mcnptm}. We adopted the SD-TMSR
core geometry optimized by Li \emph{et al.} \cite{li_optimization_2018} which
is different from the Molten Salt Breeder Reactor-like geometry by Mathieu \emph{et al.}
\cite{mathieu2006thorium} adopted by Xuemei \emph{et al.} \cite{xuemei2013study}.
Additionally, Xuemei \emph{et al.} studied the natural B$_4$C as absorbing material
while we considered six different absorbing materials.

\v{C}erba \emph{et al.} (2017) designed a reactivity control system for the 
GFR. They utilized the MCNP5 and KENO6 codes 
\cite{petrie1984keno} to calculate the reactivity worth and analyze the 
performance of this control system \cite{vcerba2017optimization}. Since no
geometry design of the control rods system is available for the SD-TMSR, 
\v{C}erba's methodology \cite{vcerba2017optimization} helped us as a starting 
point of this analysis.

@@

This paper is organized as follows: section \ref{Model-description} discusses the reactor and control rod design, section \ref{Methodology-and-tools} describes methodology and tools adopted to evaluate the control rod design, section \ref{Results-and-discussion} focuses on the results and discussion, and section \ref{Conclusion} highlights the conclusions.

>>>>

At the Beginning of Life (BOL), MSRs are commonly loaded with more
fuel than that required to achieve criticality (necessary for long-term core 
operation); this leads to excess reactivity at the BOL. Recent studies on MSRs showed that this excess reactivity 
at the BOL must be large (up to $8.1$\%) for many refueling scenarios
\cite{rykhlevskii2019modeling,betzler2016modeling,ashraf2020Strategies,ashraf2018nuclear,ashraf2020whole,ashraf2019modeling}.
Additionally, during burnup, online reprocessing and refueling system as long-term reactivity control in
the MSRs \cite{ashraf2020whole,ashraf2019Preliminary}. However, the most common and reliable procedure 
to control the reactor is to insert or withdraw control rods made of material 
with a large neutron absorption cross section (e.g., boron, cadmium) 
\cite{duderstadt650nuclear}. 
Insertion of control rods introduces negative reactivity into the 
core which helps to compensate the excess reactivity and 
adjust the power level of the core or shut down the reactor in case of 
emergency \cite{glasstone1967nuclear}. Therefore, we should estimate 
the reactivity worth of the control rods 
\cite{varvayanni2009estimation,fadaei2009control,aoyama2007core,bretscher1997computing}.
 The reactivity worth of control rods correlates with the interference 
(shadowing effects) between control rod clusters 
\cite{girardin2008development,vcerba2017optimization}. 
The control rod worth and its efficiency to absorb excess positive reactivity is a subject of major interest since it directly affects reactor safety \cite{liu2018criticality,atkinson2019small,vcerba2017optimization,do2019criticality,guo2019advanced,varvayanni2009estimation}.

@@

Xuemei \emph{et al.} (2013) calculated the control worth in the thorium molten salt
reactor by using MCNP \cite{briesmeister2000mcnptm}. We adopted the SD-TMSR
core geometry optimized by Li \emph{et al.} \cite{li_optimization_2018} which
is different from the Molten Salt Breeder Reactor-like geometry by Mathieu \emph{et al.}
\cite{mathieu2006thorium} adopted by Xuemei \emph{et al.} \cite{xuemei2013study}.
Additionally, Xuemei \emph{et al.} studied the natural B$_4$C as absorbing material
while we considered six different absorbing materials.

\v{C}erba \emph{et al.} (2017) designed a reactivity control system for the 
GFR. They utilized the MCNP \cite{briesmeister2000mcnptm} and KENO6 codes 
\cite{petrie1984keno} to calculate the reactivity worth and analyze the 
performance of this control system \cite{vcerba2017optimization}. Since no
geometry design of the control rods system is available for the SD-TMSR, 
\v{C}erba's methodology \cite{vcerba2017optimization} helped us as a starting 
point of this analysis.

@@

This paper is organized as follows: section \ref{Model-description} discusses the reactor and control rod design, section \ref{Methodology-and-tools} describes methodology and tools adopted to evaluate the control rod design, section \ref{Results-and-discussion} focuses on calculated control rod parameters such as integral and differential worth, shutdown margin (SDM), and amplification factors, and section \ref{Conclusion} highlights the conclusions.

### 2020-03-25 paper/methods.tex
after Andrei's comments

The Chinese Academy of Sciences proposed the SD-TMSR design in 2011
\cite{li_optimization_2018,jiang2012advanced,li2015analysis,li2017model}. The 
SD-TMSR is a graphite-moderated molten salt reactor with a thermal power 
of 2,250 MW$_{th}$. The design of the SD-TMSR is inspired by the 
\gls{MSBR} \cite{robertson_conceptual_1971} and the \gls{TMSR} 
\cite{nuttin2005potential} after modifying the geometry to control the 
positive moderator temperature coefficient in the MSBR. Li \emph{et al.} and Ashraf \emph{et al.}
described in detail the SD-TMSR core geometry
\cite{li_optimization_2018,ashraf2020whole}. The core of the 
SD-TMSR is a right cylinder divided into an inner zone (486 fuel tubes) 
and an outer zone (522 fuel tubes) to enhance breeding performance.

In this study, the fuel salt composition is LiF-BeF$_2$-(HM)F$_N$ (70-17.5-12.5 mol\%),
where HM is the heavy metal (i.e. $^{232}$Th and fissile 
materials), and $N$ depends on the chosen fissile material and the 
thermochemical state of the liquid fuel salt. Three different types of initial 
fissile materials are considered: (1) $^{233}$U \cite{ashraf2020whole}, 
(2) reactor-grade Pu \cite{marka1993explosive}, and (3) transuranic (TRU) 
elements from \gls{LWR} \gls{SNF} \cite{de2000scenarios}.
The density and volume of the fuel salt are 3.3 g/cm$^{3}$ and 52.9 m$^3$, 
respectively. The liquid fuel salt circulates continuously through the channels
that pierce the graphite hexagonal prisms. The core is surrounded by 
axial and radial graphite reflectors to minimize the neutron leakage.
A 10-cm-thick B$_4$C cylinder surrounds the core to shield against neutrons and heat.
Finally, the SD-TMSR pressure vessel holds all reactor components and is made of 
a Hastelloy N alloy. The main characteristics of the SD-TMSR are 
summarized in Table~\ref{tab:table1}.

\begin{table}  %[!ht]
	\caption{The main characteristics of the SD-TMSR \cite{li_optimization_2018,ashraf2020whole}.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{l | r}
		\hline
		Thermal power, MW$_{th}$          				&  2,250  \\ 
		Fuel salt components                            & LiF-BeF$_2$-(\gls{HM})F$_N$ \\
		Fuel composition, mole\%                        & 70-17.5-12.5    \\
		$^7$Li enrichment, \%        				& 99.995   \\
		Fuel temperature, K 							& 900  \\
		Fuel density at 900 K, g/cm$^3$		  		& 3.3 \\
		Dilatation coefficient, g/(cm$^3$$\cdot{}$K)  &  -6.7$\times$10$^{-4}$ \\
		Graphite density, g/cm$^3$             	    & 2.3	\\  
		Core diameter, cm								& 460  \\
		Core height, cm									& 460  \\
		Side length of the graphite hexagonal prism, cm   & 7.5 \\
		Inner radius, cm							& 3.5  \\
		Outer radius, cm							& 5  \\
		Volume ratio of molten salt to graphite \\in the inner zone	&  0.357  \\
		Volume ratio of molten salt to graphite \\in the outer zone &  1.162  \\
		Fuel volume, m$^3$  &	52.9 \\
		B$_4$C density, g/cm$^3$  &  2.54 \\
		HfB$_2$ density, g/cm$^3$  &  10.5 \\
		HfH$_{1.62}$ density, g/cm$^3$ &  11.4 \\
		Gd$_2$O$_3$ density, g/cm$^3$  &  7.04 \\
		Eu$_2$O$_3$ density, g/cm$^3$  &  7.38 \\
		SiC density, g/cm$^3$  & 3.21 \\
		AIM1 cladding density, g/cm$^3$  & 7.987 \\
		\hline
	\end{tabularx}
	\label{tab:table1}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}[b!]  % replace 't' with 'b' to \centering
	\centering
	\hspace{+0.65in} 
	\includegraphics[width=\textwidth]{cr.png}
	\caption{Cross section of the B$_4$C control rod.}
	\label{fig:cr}
\end{figure}

@@

Interference between control rods (CRs) or shadowing effects occur when one 
(or more) control rod impacts the reactivity worth of another control rod in 
the surroundings. Thus, the shadowing effect appears when the combined rod worth
is less than the sum of the individual worths. Meanwhile, anti-shadowing is observed 
when the combined rod worth is greater than the sum of the individual worths.
The core height-to-diameter ratio (H/D) and the three-dimensional configuration 
of the CRs affect the degree of the interference between CRs \cite{girardin2007control}.

@@

If A$_{CRi}$ is $<$1, the CRW is reduced due to shadowing effects, but if A$_{CRi}$ is $>$1, the CRW is amplified and anti-shadowing effects occur. A$_{CRi}$ = 1 means no shadowing effects occur.

>>>>

The Chinese Academy of Sciences proposed the SD-TMSR design in 2011
\cite{li_optimization_2018,jiang2012advanced,li2015analysis,li2017model}. The 
SD-TMSR is a graphite-moderated molten salt reactor with a thermal power 
of 2,250 MW$_{th}$. The design of the SD-TMSR is inspired by the 
\gls{MSBR} \cite{robertson_conceptual_1971} and the \gls{TMSR} 
\cite{nuttin2005potential} after modifying the geometry to control the 
positive moderator temperature coefficient in the MSBR. Li \emph{et al.} and Ashraf \emph{et al.}
described in detail the SD-TMSR core geometry
\cite{li_optimization_2018,ashraf2020whole}. Figure~\ref{fig:ff} illustrates the quarter-core view of the 
SD-TMSR. The core of the 
SD-TMSR is a right cylinder divided into an inner zone (486 fuel tubes) 
and an outer zone (522 fuel tubes) to enhance breeding performance.
\begin{figure} % replace 't' with 'b' to \centering [hbp!]
	\includegraphics[width=\textwidth]{ff.png}
	\caption{$XZ$ (a) and $XY$ (b) section of the quarter-core model of the 
		SD-TMSR \cite{ashraf2019Preliminary}.}
	\label{fig:ff}
\end{figure}
In this study, the fuel salt composition is LiF-BeF$_2$-(HM)F$_N$ (70-17.5-12.5 mol\%),
where HM is the heavy metal (i.e. $^{232}$Th and fissile 
materials), and $N$ depends on the chosen fissile material and the 
thermochemical state of the liquid fuel salt. Three different types of initial 
fissile materials are considered: (1) $^{233}$U \cite{ashraf2020whole}, 
(2) reactor-grade Pu \cite{marka1993explosive}, and (3) transuranic (TRU) 
elements from \gls{LWR} \gls{SNF} \cite{de2000scenarios}.
The density and volume of the fuel salt are 3.3 g/cm$^{3}$ and 52.9 m$^3$, 
respectively. The liquid fuel salt circulates continuously through the channels
that pierce the graphite hexagonal prisms. The core is surrounded by 
axial and radial graphite reflectors to minimize the neutron leakage.
A 10-cm-thick B$_4$C cylinder surrounds the core to shield against neutrons and heat.
Finally, the SD-TMSR pressure vessel holds all reactor components and is made of 
a Hastelloy N alloy. The main characteristics of the SD-TMSR are 
summarized in Table~\ref{tab:table1}.

\begin{table}  %[!ht]
	\caption{The main characteristics of the SD-TMSR \cite{li_optimization_2018,ashraf2020whole}.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{l | r}
		\hline
		Thermal power, MW$_{th}$          				&  2,250  \\ 
		Fuel salt components                            & LiF-BeF$_2$-(\gls{HM})F$_N$ \\
		Fuel composition, mole\%                        & 70-17.5-12.5    \\
		$^7$Li enrichment, \%        				& 99.995   \\
		Fuel temperature, K 							& 900  \\
		Dilatation coefficient, g/(cm$^3$$\cdot{}$K)  &  -6.7$\times$10$^{-4}$ \\ 
		Fuel volume, m$^3$  &	52.9 \\
		Fuel density at 900 K, g/cm$^3$		  		& 3.3 \\
		Graphite density, g/cm$^3$             	    & 2.3	\\ 
		B$_4$C density, g/cm$^3$  &  2.54 \\
		HfB$_2$ density, g/cm$^3$  &  10.5 \\
		HfH$_{1.62}$ density, g/cm$^3$ &  11.4 \\
		Gd$_2$O$_3$ density, g/cm$^3$  &  7.04 \\
		Eu$_2$O$_3$ density, g/cm$^3$  &  7.38 \\
		SiC density, g/cm$^3$  & 3.21 \\
		AIM1 cladding density, g/cm$^3$  & 7.987 \\
		Core diameter, cm								& 460  \\
		Core height, cm									& 460  \\
		Side length of the graphite hexagonal prism, cm   & 7.5 \\
		Radius (inner fuel channel), cm							& 3.5  \\
		Radius (outer fuel channel), cm							& 5  \\
		Volume ratio of molten salt to graphite \\in the inner zone	&  0.357  \\
		Volume ratio of molten salt to graphite \\in the outer zone &  1.162  \\

		\hline
	\end{tabularx}
	\label{tab:table1}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}[t!]  % replace 't' with 'b' to \centering
	\centering
	\hspace{+0.65in} 
	\includegraphics[width=\textwidth]{cr.png}
	\caption{Cross section of the B$_4$C control rod.}
	\label{fig:cr}
\end{figure}

@@

Interference between control rods (CRs) or shadowing effects occur when one 
(or more) control rod impacts the reactivity worth of another control rod in 
the surroundings. 
The insertion of a CR depresses the neutron flux
in its vicinity and makes the curvature of the neutron flux greater. The gradient
of the neutron flux will contrarily increase at a radial distance. The CRs, distributed in the core,
will distort the neutron flux around each other and will impact the reactivity worth.
The term ``shadowing effect" has been used to describe this \cite{oka2014nuclear}.
The shadowing effect appears when the combined rod worth
is less than the sum of the individual worths. Meanwhile, anti-shadowing is observed 
when the combined rod worth is greater than the sum of the individual worths.
The core height-to-diameter ratio (H/D), CR locations, and the three-dimensional configuration 
of the CRs affect the degree of the interference between CRs \cite{oka2014nuclear,girardin2007control}.

@@

If A$_{CRi}$ is $<$1, the CRW is reduced due to shadowing effects, but if A$_{CRi}$ is $>$1, the CRW is amplified and anti-shadowing effects occur \cite{girardin2007control}. A$_{CRi}$ = 1 means no shadowing effects occur.
